---
title:  "GTA Vehicle Analysis"
author: "Lucas Okwudishu"
date:   "2023-02-01"
output: html_document
theme:  flatly 
highllight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 6, 
                      fig.asp = 0.8, out.width = "60%")
```

## Introduction

Grand Theft Auto V (GTA V) is an action packed open world game developed by Rockstar Games.
While its been a few years since I picked up my ps4, I'm still a huge fan of the game and have
many fond memories from spending hours only playing with people from around the world. Thus
when I got the opportunity to combine my love for the game with my love data analysis, I jumped on it.

Recently I've been dabbling in web scraping and as part of practice, I decided to 
scrape GTA V vehicle information from [gtabase.com](). While there are a total of
708 vehicles currently in GTA V, my web scraping script was only able to retrieve data
for about 580 vehicles. There remain urls appeared to error out. If you're interested
in the script I used to scrape the data, take a look at [this]() file in my github 
repo. The script can definitely be improved on, but it did the job for me. Additionally,
if you're want to see the links that failed and wish to attempt to scrape data
for those vehicles, you can find that list [here]().

While the vehicles in this analysis fell into 20 categories from planes to emergency vehicles,
I was only interested on land vehicles that fell into the following categories;
SUVs, Motorcycles, Sedans, Sports Classics, Off-Road, Sports, Super, Muscle, Coupes, and
compacts. After filtering for these categories, the number of vehicles left to work
with was 421.

Some things I was interested in understanding;

* What are the most expensive vehicles
* How does price of vehicles differ by vehicle class, manufacturer, etc
* How does price of vehicles differ by speed
* How does speed of vehicles differ by vehicle class, manufacturer, etc
* What vehicles have the best resale value

>>> Lets dive in...

## Vehicle Count by Class

```{r}
knitr::include_graphics("../png/count_by_class")

```


Sport cars dominate the land vehicle landscape in GTA V. If you have a need for speed,
this is the game for you. 

---

## Vehicle Count by Manufacturer

```{r}
knitr::include_graphics("../png/p2_count_by_manufacturer")
```

Top 10 manufactures account for 50% of vehicles in this dataset.

---

## Vehicle Count by Release DLC

```{r}
knitr::include_graphics("../png/p3_count_by_release_dlc")
```

28% of vehicles in this dataset were released at game launch. Beyond the release
DLC, these chart shows when majority of current vehicles were released.

---

>>> Show me the money!

---

## Price vs Vehicle Class

- Insert Chart 

If you want to cruise around in a cool super car or sports car, be read to drop some
coin. 

<!-- --- -->
<!-- ## Price vs Number of Features -->
<!-- ** Insert Chart -->
<!-- Number of features in a vehicle does not appear to be be correlated with price. -->
<!-- --- -->

<!-- ## Top 10 Expensive Cars vs Manufacturer -->
<!-- - Insert Chart  -->

<!-- --- -->

<!-- >>> Whats what's the most expensive car in GTA V? -->

<!-- ** List car here ** -->

<!-- --- -->
<!-- ## Best Resale Value -->
<!-- --- -->

<!-- ## Speed -->
<!-- * Top 10 speed by vehicle class -->
<!-- * Top 10 lap time by vehicle class -->

<!-- --- -->

<!-- ## Correlations  -->
<!-- * Examine correlations of numeric features with price -->




